Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-25 doc/main_jfm.tex
conclusion draft

>>>>

This study proposes a continuum coarse-grained model for Janus-vesicle that focuses on the 
hydrophobic interactions between lipids and hydrodynamic interactions.
The mobility problem using integral equation methods combines the previously introduced HAP and the 
revised hydrophobic force for obtaining particle dynamics. 
The imposed forces and torques of Janus particles adopt not only HAP but a newly developed short 
range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.

With the use of selected parameters, the numerical algorithm yields good qualitative results such as
phenomena in tank-treading Janus-vesicle and asymmetric slipper shape in a parabolic flow. 
We also demonstrate the membrane rupture in a flow at high shear rate and this makes a breakthrough 
about having an idea for simulating such phenomenon different from other continuum modeling simulations.
Inter-monolayer friction coefficients are then obtained and reported by calculating the pressure jumps and
slip velocities with respect to the bilayer midplane.
Results of two Janus-vesicles in flow simulations produce an outstanding agreement with ones generated 
using continuum modeling.

Our future goal is to extend the current framework to a three-dimensional Janus-vesicle system. 
The further implementation of adding a fast algorithms such as the fast multipole method is also a 
practical approach.
